---
title: "P8105 HW01"
output: github_document
   
---

## Problem 1a

```{r Problem 1a}

library(tidyverse)
set.seed(1)

hw1_df = tibble(
  ## creating a random sample of size 8 normally distributed
  rand_samp = rnorm(8), 
  
  ## is the random sample value greater than 0 in logic form
  samp_vec_gtr = rand_samp>0,  
  
  ## character vector with 8 elements
  char_vec = c("I","am","hoping","this","homework","structure","is","correct"), 
  
  ## factor vector of length 8 and 3 different levels
  fac_vec=factor(c("sam", "I", "am", "I", "am", "am", "I", "sam"))
  
)

mean(pull(hw1_df,rand_samp))
mean(pull(hw1_df,samp_vec_gtr))
mean(pull(hw1_df,char_vec))
mean(pull(hw1_df,fac_vec))
```

**1a code responses:**

The mean function works for the random normal distribution sample and the logic vector but not the character or factor vectors

### **Problem 1b**

```{r Problem 1b,eval=FALSE}
as.numeric(pull(hw1_df,samp_vec_gtr))
as.numeric(pull(hw1_df,char_vec))
as.numeric(pull(hw1_df,fac_vec))
```

```{r}
logic_vec_num=as.numeric(pull(hw1_df, samp_vec_gtr))
log_times_rand=(pull(hw1_df,rand_samp))*logic_vec_num

logic_factor=factor(logic_vec_num)
fac_times_rand=(pull(hw1_df,rand_samp))*logic_factor

logic_factor_num=(pull(hw1_df,rand_samp))*(as.numeric(logic_factor))


```

**Problem 1 Responses**
Trying to return mean for the variables produces values for the normal distribution and logic variable but not the character or factor variables. When looking at these variables from the as.numeric function, it makes sense. The distribution variables are numbers and thus has a mean. The logic variable can be represented by 0/1 and will have a mean when using that method of indicating true/false. The character variable does not have any number associated with each element in the vector. Thus it will not have a mean. The factor variable is the only odd one. It does have an as.numeric value because each element returns their "level" as the numeric but since these numbers are categories and not values, it does not return a mean value.


## Problem 2
```{r}
set.seed(1)

prob2_df=tibble(
  x=rnorm(500),
  y=rnorm(500),
  logic_x_y=(x+y)>1,
  num_logic=as.numeric(logic_x_y),
  fac_vec=factor(logic_x_y)
)




```


The data frame from problem 2 has a size of `r nrow(prob2_df)` rows and `r ncol(prob2_df)`  columns. 

The x variable has a mean of `r mean(pull(prob2_df,x))`, median of `r mean(pull(prob2_df,x))`, and a standard deviation of `r sd(pull(prob2_df,x))`.

X+Y was greated than 1 `r sum(pull(prob2_df,num_logic))/500*100`percent.

```{r}
ggplot(
  prob2_df, 
  aes(x = x, y = y,color=logic_x_y)) + geom_point()

ggsave("firstggplot.jpeg")

ggplot(
  prob2_df, 
  aes(x = x, y = y,color=num_logic)) + geom_point()

ggplot(
  prob2_df, 
  aes(x = x, y = y,color=fac_vec)) + geom_point()

```


